A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-11-03 bioc-workflow.Rnw
thresholding section

Deciding on a threshold is not trivial as classifier scores are
heavily dependent upon the classifier used and different sub-cellular
niches can exhibit different score distributions, as highlighted in
the boxplot below. We recommend users to set class-specific
thresholds.  In the code chunk below we display a boxplot of the score
distributions per organelle.

@@

The output of \texttt{getPredictons} is the original \texttt{MSnSet}
dataset with a new feature variable appended to the feature data
called \texttt{fcol.pred} (i.e. in our case \texttt{svm.pred})
containing the prediction results. The results can also be visualied
using \texttt{plot2D} function.

@@

\begin{figure}[!ht]
    \centering
<<plotres, out.width=".8\\textwidth">>=
plot2D(hl, fcol = "svm.pred")
@  
  \caption{Results of the localisation preductions after thresholding.}
  \label{fig:plotres}
\end{figure}

There is also a dedicated interactive application to help users
examine these distributions in the \Biocpkg{pRolocGUI} package.
This app can be launched via the \texttt{pRolocVis} function and specifying
the argument \texttt{app = "classify"} along with the relevent \texttt{fcol}, \texttt{scol}
and \texttt{mcol} which refer to the columns in the feature data that contain
the new assignments, assignment scores and markers respectively (see
also \texttt{fvarLabels(svmres)}).

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{./Figures/classify.png}
  \caption{The classify application}
  \label{fig:classifyapp}
\end{figure}

The data is loaded and displayed on a PCA plot and a boxplot is used
to display the classifier scores by data class. On the left there is a
sidebar panel with sliders to control the thresholds upon which
classifications are made. There are two types of cut-off that the user
can choose from: (1) "Quantile" and (2) "User-defined". By default,
when the application is launched quatile scoring is selected and set
to 0.5, the median. The class-specific score thresholds that
correspond to selecting the desired quantile are shown on as red dots
on the boxplot. The assignments on the PCA plot are also updated
according to the selected threshold. The quantile threshold can be set
by moving the corresponding quantile slider. If one wished to set
their own cut-offs the "User-defined" radio button must be selected
and then the sliders for defining user-specified scores become active
and the scores and highlighted on the boxplot by blue dots. For more
information we refer users to the \Biocpkg{pRolocGUI}
tutorial
\href{http://bioconductor.org/packages/release/bioc/vignettes/pRolocGUI/inst/doc/pRolocGUI.html}{vignette}.

>>>>

Deciding on a threshold is not trivial as classifier scores are
heavily dependent upon the classifier used and different sub-cellular
niches can exhibit different score distributions, as highlighted in
the boxplot below. We recommend users to set class-specific
thresholds.  In the code chunk below we display a boxplot of the score
distributions per organelle (Figure \ref{fig:threshold}).

@@

The output of \texttt{getPredictons} is the original \texttt{MSnSet}
dataset with a new feature variable appended to the feature data
called \texttt{fcol.pred} (i.e. in our case \texttt{svm.pred})
containing the prediction results. The results can also be visualied
using \texttt{plot2D} function (Figure \ref{fig:plotres}).

@@

\begin{figure}[!ht]
    \centering
<<plotres, out.width=".7\\textwidth">>=
plot2D(hl, fcol = "svm.pred")
@  
  \caption{Results of the localisation preductions after thresholding.}
  \label{fig:plotres}
\end{figure}

There is also a dedicated interactive application to help users
examine these distributions in the \Biocpkg{pRolocGUI} package (Figure
\ref{fig:classifyapp}).  This app can be launched via the
\texttt{pRolocVis} function and specifying the argument \texttt{app =
  "classify"} along with the relevent \texttt{fcol}, \texttt{scol} and
\texttt{mcol} which refer to the columns in the feature data that
contain the new assignments, assignment scores and markers
respectively (see also \texttt{fvarLabels(svmres)}).

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=0.7\textwidth]{./Figures/classify.png}
  \caption{The classify application enable the interactive exploration
    of classification score thresholding.}
  \label{fig:classifyapp}
\end{figure}

The data is loaded and displayed on a PCA plot and a boxplot is used
to display the classifier scores by data class. On the left, there is
a sidebar panel with sliders to control the thresholds upon which
classifications are made. There are two types of cut-off that the user
can choose from: (1) \textit{Quantile} and (2)
\textit{User-defined}. By default, when the application is launched
quatile scoring is selected and set to 0.5, the median. The
class-specific score thresholds that correspond to selecting the
desired quantile are shown on as red dots on the boxplot. The
assignments on the PCA plot are also updated according to the selected
threshold. The quantile threshold can be set by moving the
corresponding quantile slider. If one wished to set their own cut-offs
the \textit{User-defined} radio button must be selected and then the
sliders for defining user-specified scores become active and the
scores and highlighted on the boxplot by blue dots. For more
information we refer users to the \Biocpkg{pRolocGUI} tutorial
\href{http://bioconductor.org/packages/release/bioc/vignettes/pRolocGUI/inst/doc/pRolocGUI.html}{vignette}.
